Summary Tables

### 2019-05-13 summary_tables.Rmd

>>>>

    count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
    td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
